---
title: Pupil size analysis of action prediction elephant experiment
date: "25/12/2021"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#rm(list=ls())
library(tidyverse)
library(summarytools)
library(exactRankTests)
library(lme4)
library(naniar)
#install.packages("remotes")
#remotes::install_github("dmirman/gazer")
library(gazer) 
library(zoo)
library(itsadug)
source("functions/diagnostic_fcns.r")
source("functions/glmm_stability.r")
source("functions/boot_glmm.r")

library(itsadug)
packageVersion("itsadug")
library(plotfunctions)
packageVersion("plotfunctions")
library(colorspace)
packageVersion("colorspace")
## Define colors:
col1 <- 'pink1'
col2 <- 'black'
col3 <- 'indianred'

```

### Loading data
```{r}
## time.frame for interpolation
max.time <- 8000
min.time <- 0
time <- seq(from = min.time, to = max.time, by = 1)
xx <- as.data.frame(time)

baseline.end<-200


demo_data<-read.csv(file="data/AP_elephant_counterbalancing_order.csv")%>%
    select(-subject)%>%
  rename(subject="Name")
  
#select(-Name)
#%>%rename(subject="Name")

sample.data <- read_delim("data/elephant_final_sample_report.txt", na=".", delim="\t")%>%
  mutate(Session_Name=recode_factor(RECORDING_SESSION_LABEL, Georgia2="Georgia_2",Georgia1="Georgia_1", Georgia3="Georgia_3", Schnee1="Schnee_1", Georgia4="Georgia_4"))%>%
  mutate(TRIAL_INDEX=as.numeric(ifelse(RECORDING_SESSION_LABEL=="Georgia4", TRIAL_INDEX+3, ifelse(RECORDING_SESSION_LABEL=="Ace_2",TRIAL_INDEX+1,TRIAL_INDEX))))%>%#fix the trial number
  separate(Session_Name, c("subject", "session.num"), sep = "_") %>%
  full_join(demo_data) %>%
  #filter(!is.na(session.num))%>%
  mutate(time = TIMESTAMP - IP_START_TIME)


str(sample.data)
levels(as.factor(sample.data$condition))

min(sample.data$TIMESTAMP)
min(sample.data$time)
max(sample.data$time)

table(sample.data$condition, sample.data$RECORDING_SESSION_LABEL)
table(sample.data$condition, sample.data$subject)
table(sample.data$RECORDING_SESSION_LABEL, sample.data$TRIAL_INDEX)
```



### Pupil size

#### Artefact check
*Plot raw data
```{r eval=FALSE}
raw_plot_pupil<-ggplot(data = sample.data, aes(x = time, y = RIGHT_PUPIL_SIZE)) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_point(aes(color = condition), alpha = 0.3, size = 0.5) +
  facet_grid(TRIAL_INDEX~subject)+
  xlim(0, 8000) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue", "darkgreen"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue", "darkgreen"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = "bottom"#c(0.65, 0.1)
        , legend.text=element_text(size=12))
raw_plot_pupil
```


```{r eval=FALSE}
ggsave(raw_plot_pupil, filename = "graphics/pupil_raw_plot.png", width=14, height=8, scale=0.8)
```
* Plot with blink artefacts removed
```{r }
sample.data<-sample.data%>%
        mutate(RIGHT_PUPIL_SIZE_no_blinks=extend_blinks(RIGHT_PUPIL_SIZE,  hz=1000, fillback=100, fillforward=100))#Extends blinks


artefact_check<-ggplot(data = sample.data,
  aes(x = time, y = RIGHT_PUPIL_SIZE_no_blinks)) +
  ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_point(aes(color = condition), alpha = 0.1, size = 0.5) +
  facet_grid(TRIAL_INDEX~subject)+
  xlim(0, 8000) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue", "darkgreen"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue", "darkgreen"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position ="none")

artefact_check
```


```{r }
ggsave(artefact_check, filename = "graphics/pupil_blinks_removed.png", width=15, height=8)
```

proportion of valid data
```{r}

prop.tracked.data<-sample.data%>%
  #mutate(subj_con_trial=paste(subject, condition, TRIAL_INDEX))%>%
  group_by(subject, condition, TRIAL_INDEX)%>%
  summarise(length=length(RIGHT_PUPIL_SIZE_no_blinks), sum_noNA=sum(!is.na(RIGHT_PUPIL_SIZE_no_blinks)), prop=sum(!is.na(RIGHT_PUPIL_SIZE_no_blinks))/length(RIGHT_PUPIL_SIZE_no_blinks), min(RIGHT_PUPIL_SIZE), max(RIGHT_PUPIL_SIZE))

prop.tracked.data%>%group_by(condition)%>%summarise(min(prop))



prop.tracked.gaze.data<-sample.data%>%
  filter(time<=3230)%>%
  filter(RIGHT_GAZE_X<1024&RIGHT_GAZE_X>0&RIGHT_GAZE_Y<768&RIGHT_GAZE_Y>0)%>%
  group_by(subject, condition, TRIAL_INDEX)%>%
  summarise(prop=sum(!is.na(RIGHT_GAZE_X))/max(time))

which(prop.tracked.gaze.data$prop<0.7)
#filter out subjects with onscreen gaze data <70%
sample.data<-sample.data%>%
  filter(!(subject=="Amy" & TRIAL_INDEX==3 & condition=="human_within"))%>%
  filter(!(subject=="Maylo" & TRIAL_INDEX==1 & condition=="human_within"))%>%
  filter(!(subject=="Zserbo" & TRIAL_INDEX==3 & condition=="human_within"))

```


* Plot distribution of pupil sizes
```{r eval=FALSE}
puphist <- ggplot(sample.data, aes(x = RIGHT_PUPIL_SIZE_no_blinks)) + geom_histogram(aes(y = ..count..), 
    colour = "green", binwidth = 0.5)  + 
    xlab("Pupil Size") + ylab("Count") + theme_bw() 
puphist
```

#### Preprocessing: interpolation, baseline correction, down sampling
```{r}
# determine baseline
exp.data.pupil.base <- sample.data %>%
  filter(time < baseline.end & time > 0) %>% 
    group_by(subject, condition) %>%
  summarise(median.base.pupil = median(RIGHT_PUPIL_SIZE_no_blinks, na.rm = TRUE))

#preprocessing
exp.data.pupil.processed <- sample.data %>%
  filter(time<max.time)%>%
  select(subject, time, condition, TRIAL_INDEX, RIGHT_GAZE_X, RIGHT_GAZE_Y, RIGHT_PUPIL_SIZE_no_blinks) %>%
  group_by(subject, condition, TRIAL_INDEX, time) %>%
  full_join(xx%>%select(time)) %>% #add missing time.frames
  ungroup() %>%
  group_by(subject, condition, TRIAL_INDEX) %>%
  mutate(pupil.inter = na.approx(RIGHT_PUPIL_SIZE_no_blinks, na.rm = FALSE, maxgap = 500)) %>% #linear interpolation
  full_join(exp.data.pupil.base) %>% #add baseline data
  mutate(pupil.base.corrected = pupil.inter - median.base.pupil)%>% #subtractive baseline correction
  ungroup()%>%
    mutate(bin = cut(time, seq(min(time), max(time), 100), right = FALSE))%>% #addition of time bins (100 ms = 10 hz)
  separate(bin, c("bin_low", "bin_high"), sep=",", remove=FALSE)%>%
  select(-bin_high)%>%
  mutate(bin_low=as.numeric(str_replace_all(bin_low, "\\[|\\]", "")))
  
#down sampling to 10hz using median values:
exp.data.pupil.processed.downsampled <- exp.data.pupil.processed %>%  
  group_by(subject, condition, TRIAL_INDEX, bin_low)%>%
  summarise(pupil.base.corrected.binned=median(pupil.base.corrected), Xgaze=median(RIGHT_GAZE_X), Ygaze=median(RIGHT_GAZE_Y))%>%
  ungroup()

levels(as.factor(exp.data.pupil.processed.downsampled$TRIAL_INDEX))
levels(as.factor(exp.data.pupil.processed.downsampled$subject))
```


* Plot interpolated data: individual level
```{r}
plot.pupil.individual<-ggplot(data = exp.data.pupil.processed.downsampled, aes(x = bin_low, y =pupil.base.corrected.binned )) +
  ylab("Pupil size ") +
  xlab("Time (in ms)") +
    geom_vline(aes(xintercept=baseline.end), lty=2, alpha=0.3)+
  geom_point(aes(color = condition), alpha = 0.8, size = 0.5) +
  geom_line(aes(color = condition), alpha = 0.8) +
  facet_grid(TRIAL_INDEX~subject)+
  xlim(0, 8000) +
    theme_bw()+
  scale_color_manual(values=c("darkorange", "dodgerblue", "darkgreen"))+
  scale_fill_manual(values=c("darkorange", "dodgerblue", "darkgreen"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = "none")

plot.pupil.individual

#ggsave(plot.contact.pupil.individual, filename = "graphics/plot.contact.pupil_baseline_corrected_individual.png", height = 7, width = 8, scale = 0.8)
```

* Plot group level data
```{r}
pupil.group.level <- exp.data.pupil.processed.downsampled %>%
  group_by(bin_low, condition) %>%
  summarise(mean.pupil.corrected.binned = mean(pupil.base.corrected.binned, na.rm = TRUE), sd.pupil.corrected.binned= sd(pupil.base.corrected.binned, na.rm = TRUE), se.pupil.corrected.binned = sd(pupil.base.corrected.binned, na.rm = TRUE) / sqrt(length(pupil.base.corrected.binned)))%>%
filter(!is.na(condition))%>%
mutate(condition=recode(condition, "human_outside"="Human outside", "human_within"="Human within", "dog"="Dog"))

plot.elephant.pupil <- ggplot(data = pupil.group.level, aes(x = bin_low, y = mean.pupil.corrected.binned)) +
  geom_vline(aes(xintercept=baseline.end), lty=2, alpha=0.3)+
    ylab("Pupil size") +
  xlab("Time (in ms)") +
  geom_point(aes(x = bin_low, y = mean.pupil.corrected.binned, color = condition), alpha = 0.3, size = 0.5) +
  geom_ribbon(aes(ymin = mean.pupil.corrected.binned - se.pupil.corrected.binned, ymax = mean.pupil.corrected.binned + se.pupil.corrected.binned, fill = condition), alpha = 0.3) +
    xlim(0, 8000) +
    theme_bw()+
  scale_color_manual(values=c("dodgerblue", "darkgreen","darkorange"))+
  scale_fill_manual(values=c("dodgerblue", "darkgreen","darkorange"))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank(), legend.position = c(0.80, 0.30), legend.text=element_text(size=12))

plot.elephant.pupil
```


```{r}
ggsave(plot.elephant.pupil, filename = "graphics/pupil_gaze_corrected_200bl.png", height = 5, width = 8, scale = 0.7)
```
### GAMM

* Plot gaze positions
```{r}
emptyPlot(c(0,1024), c(768, 0), bty='o',
          main="Gaze positions", xlab="Xgaze", ylab="Ygaze")
points(exp.data.pupil.processed.downsampled$Xgaze, exp.data.pupil.processed.downsampled$Ygaze, pch=16, cex=.5, col=alpha(1), xpd=TRUE)
abline(h=768/2, v=1024/2, lty=1, col='white')
abline(h=768/2, v=1024/2, lty=2, col=1)
```

* Plot pupil size by subject
```{r}
par(cex=1.1)
bp <- sortBoxplot(exp.data.pupil.processed.downsampled$pupil.base.corrected.binned ~ exp.data.pupil.processed.downsampled$subject, col=alpha(1), decreasing=FALSE,
                  ylab="Pupil size", xlab="Subject", bty='n', pch=".")


```

#### data preparation for GAMM

* select interest period
```{r}
dat <- exp.data.pupil.processed.downsampled%>%
  filter(bin_low >= 3000 & bin_low <= 7000)%>% #select interest period
  rename(pupil_base="pupil.base.corrected.binned", time="bin_low")%>%
  arrange(subject, condition, TRIAL_INDEX, time)%>%#order dataframe
  droplevels()

dat$condition<-as.factor(dat$condition)

levels(dat$condition)
dat$subject<-as.factor(dat$subject)
summary(dat)
```



#### fitting GAMM

```{r}
# Defining events (time series):
dat$Event <- interaction(dat$subject, dat$condition, dat$TRIAL_INDEX, drop=TRUE)

m2 <- bam(pupil_base ~ condition + s(time, k=20)+ s(time, by=condition, k=20) 
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat, discrete=TRUE, nthreads=40, method="ML")

m2.null <- bam(pupil_base ~ s(time, k=20)+ 
          + s(Xgaze, Ygaze)
          + s(time, Event, bs='fs', m=1)
          , data=dat, discrete=TRUE, nthreads=40, method="ML")
summary(m2)

gam.check(m2)

acf(resid(m2), bty='n', main="ACF residuals model1")
acf(resid(m2), plot=FALSE)

compareML(m2.null, m2)
AIC(m2, m2.null)
```



```{r}
#save gam_check
#install.packages("remotes")
remotes::install_github("m-clark/visibly")
library(visibly) 
png("graphics/GAMM01_gam_check.png", units="cm", res=600, width=24, height = 18)
gam_check_plot<-plot_gam_check(m2, scatter=TRUE)
print(gam_check_plot)
dev.off()

png("graphics/GAMM01_acf_plot.png", units="cm", res=600, width=12, height = 12)
acf_plot<-acf(resid(m2), bty='n', main="")
print(acf_plot)
dev.off()
```


* difference curve
```{r}
#save data

plot_diff_m2_dog_hw<-plot_diff(m2, view="time", 
          comp=list(condition=c("dog", "human_within")), rm.ranef=TRUE, 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = FALSE)


plot_diff_m2_dog_ho<-plot_diff(m2, view="time", 
          comp=list(condition=c("dog", "human_outside")), rm.ranef=TRUE, 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = FALSE)

plot_diff_m2_hw_ho<-plot_diff(m2, view="time", 
          comp=list(condition=c("human_within", "human_outside")), rm.ranef=TRUE, 
          las=1, ylab="Est. difference in pupil size", 
            col=col2, hide.label = TRUE, plot = FALSE)

plot_diff_m2_dog_hw<-ggplot(data=plot_diff_m2_dog_hw, aes(x=time, y=est))+
  geom_hline(yintercept = 0)+
  geom_path(lty=2)+
  geom_ribbon(aes(x=time, ymin=est-CI, ymax=est+CI), alpha=0.2)+
  theme_bw()+
  #ylim(-200, 800)+
  scale_x_continuous(name="Time (in ms)", breaks=c(3000, 4000, 5000, 6000))+ ylab("Est. difference in pupil size")+ggtitle("Dog - Human-within")+
    theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

plot_diff_m2_dog_ho<-ggplot(data=plot_diff_m2_dog_ho, aes(x=time, y=est))+
  geom_hline(yintercept = 0)+
  geom_path(lty=2)+
  geom_ribbon(aes(x=time, ymin=est-CI, ymax=est+CI), alpha=0.2)+
  theme_bw()+
  #ylim(-200, 800)+
  scale_x_continuous(name="Time (in ms)", breaks=c(3000, 4000, 5000, 6000))+ ylab("Est. difference in pupil size")+ggtitle("Dog - Human-outside")+
    theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

plot_diff_m2_hw_ho<-ggplot(data=plot_diff_m2_hw_ho, aes(x=time, y=est))+
  geom_hline(yintercept = 0)+
  geom_path(lty=2)+
  geom_ribbon(aes(x=time, ymin=est-CI, ymax=est+CI), alpha=0.2)+
  theme_bw()+
  scale_x_continuous(name="Time (in ms)", breaks=c(3000, 4000, 5000, 6000))+ ylab("Est. difference in pupil size")+ggtitle("Human-within - Human-outside")+
    theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

library(cowplot)
pg_m2<-plot_grid(plot_diff_m2_dog_hw, plot_diff_m2_dog_ho, plot_diff_m2_hw_ho, nrow=1, labels=c("B", "C", "D"))


ggsave(pg_m2, filename = "graphics/pupil_diff_m2_gg.png", width=18, height=6, scale=0.6)

```

* plotting partial effects
```{r}
pdf("graphics/AP_elephant_m2_GAMM_partical_effect.pdf", width=10, height = 8)
plot(m2, pages = 1, all.terms = TRUE, residuals = TRUE, rug=FALSE, pch = 1, cex = 0.5, seWithMean = TRUE, shade = TRUE, shade.col = "lightblue")
dev.off()

library(mgcViz)
b <- getViz(m2)
png("graphics/AP_elephant_m2_GAMM_partical_effect2.png", units="cm", res=600, width=24, height = 16)
p1<-plot(b, allTerms = T)+theme_classic() + labs(title = NULL)
print(p1, pages = 1 )
dev.off()

```


* Summed effects
```{r}

plot_smooth(m2, view="time", cond=list(condition="dog"), rm.ranef=TRUE,
  v0=0, col=col2, lwd=2, lty=6, rug=FALSE, se=1.96,
  main="Estimated effects", ylab="Pupil (baselined)", las=1)

plot_smooth(m2, view="time", cond=list(condition="human_within"), rm.ranef=TRUE,
  v0=0, col=col2, lwd=2, lty=6, rug=FALSE, se=1.96,
  main="Estimated effects", ylab="Pupil (baselined)", las=1)
plot_smooth(m2, view="time", cond=list(condition="human_outside"), rm.ranef=TRUE,
  v0=0, col=col2, lwd=2, lty=6, rug=FALSE, se=1.96,
  main="Estimated effects", ylab="Pupil (baselined)", las=1)
```

```{r}

tmp <- m2$model
plot_modelfit(m2, view="time", event=tmp$Event,n = 2)

```




#### Creating plot grid
```{r}
library(cowplot)

pg_elephant<-plot_grid(plot.elephant.pupil,pg_m2, rel_widths = c(2,0.5), rel_heights=c(1,0.7), labels=c("A"), ncol=1)
pg_elephant

ggsave(pg_elephant, filename = "graphics/pupil_size_plots.png", width=12, height=9, scale=0.8, dpi=1200)

```



## Plot gaze data
*Interpolate dynamic IA values

```{r}
ai.data<- read_csv("data/VoE_contact_dynamic_IAs.csv") %>%
  mutate(x_average = (x_l + x_r) / 2, y_average = (y_up + y_low) / 2, time.frame = start)

ai.data.launch<-ai.data%>% filter(label=="launch_ball")
ai.data.launch.hab<-ai.data%>% filter(label=="launch_ball_hab")
ai.data.target.exp<-ai.data%>% filter(label=="target_ball_exp")
ai.data.target.con<-ai.data%>% filter(label=="target_ball_con")

```

```{r}

library(zoo)
## interpolation

#launch ball
max.time <- max(ai.data.launch$end)
min.time <- min(ai.data.launch$start)
time.frame <- seq(from = min.time, to = max.time, by = 1)
xx <- as.data.frame(time.frame)

launch.ball.data <- xx %>%
  full_join(ai.data.launch, by = "time.frame") %>%
  mutate(x_approx = na.approx(x_average), y_approx = na.approx(y_average), x_l_approx = na.approx(x_l), y_up_approx = na.approx(y_up), x_r_approx = na.approx(x_r), y_low_approx = na.approx(y_low))

#launch ball habituation
max.time <- max(ai.data.launch.hab$end)
min.time <- min(ai.data.launch.hab$start)
time.frame <- seq(from = min.time, to = max.time, by = 1)
xx <- as.data.frame(time.frame)

launch.ball.data.hab <- xx %>%
  full_join(ai.data.launch.hab, by = "time.frame") %>%
  mutate(x_approx = na.approx(x_average), y_approx = na.approx(y_average), x_l_approx = na.approx(x_l), y_up_approx = na.approx(y_up), x_r_approx = na.approx(x_r), y_low_approx = na.approx(y_low))

#target ball exp
max.time <- max(ai.data.target.exp$end)
min.time <- min(ai.data.target.exp$start)
time.frame <- seq(from = min.time, to = max.time, by = 1)
xx <- as.data.frame(time.frame)

target.ball.data.exp <- xx %>%
  full_join(ai.data.target.exp, by = "time.frame") %>%
  mutate(x_approx = na.approx(x_average), y_approx = na.approx(y_average), x_l_approx = na.approx(x_l), y_up_approx = na.approx(y_up), x_r_approx = na.approx(x_r), y_low_approx = na.approx(y_low))


#target ball con
max.time <- max(ai.data.target.con$end)
min.time <- min(ai.data.target.con$start)
time.frame <- seq(from = min.time, to = max.time, by = 1)
xx <- as.data.frame(time.frame)

target.ball.data.con <- xx %>%
  full_join(ai.data.target.con, by = "time.frame") %>%
  mutate(x_approx = na.approx(x_average), y_approx = na.approx(y_average), x_l_approx = na.approx(x_l), y_up_approx = na.approx(y_up), x_r_approx = na.approx(x_r), y_low_approx = na.approx(y_low))

```

* prepare data for gaze plotting
```{r}
gaze_plot_data <- exp.data.pupil.processed.downsampled %>%
  filter(bin_low < 13501 ) %>%
  group_by(bin_low, condition) %>%
  summarise(mean.x = mean(Xgaze, na.rm=TRUE), median.x = median(Xgaze,  na.rm=TRUE), se.x = sd(Xgaze, na.rm=TRUE) / sqrt(length(Xgaze))) %>%
  mutate(time.frame=bin_low)%>%
 left_join(launch.ball.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch=x_l_approx, x_r_launch=x_r_approx, x_launch=x_approx))%>%
  left_join(launch.ball.data.hab%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch_hab=x_l_approx, x_r_launch_hab=x_r_approx, x_launch_hab=x_approx))%>%
  left_join(target.ball.data.exp%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_exp=x_l_approx, x_r_target_exp=x_r_approx, x_target_exp=x_approx))%>%
  left_join(target.ball.data.con%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_con=x_l_approx, x_r_target_con=x_r_approx, x_target_con=x_approx))



gaze_plot_data_subject <- exp.data.pupil.processed.downsampled %>%
  filter(bin_low < 13501 ) %>%
  group_by(bin_low, condition, subject) %>%
  summarise(mean.x = mean(Xgaze, na.rm=TRUE), median.x = median(Xgaze,  na.rm=TRUE), se.x = sd(Xgaze, na.rm=TRUE) / sqrt(length(Xgaze))) %>%
  mutate(time.frame=bin_low)%>%
 left_join(launch.ball.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch=x_l_approx, x_r_launch=x_r_approx, x_launch=x_approx))%>%
  left_join(launch.ball.data.hab%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch_hab=x_l_approx, x_r_launch_hab=x_r_approx, x_launch_hab=x_approx))%>%
  left_join(target.ball.data.exp%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_exp=x_l_approx, x_r_target_exp=x_r_approx, x_target_exp=x_approx))%>%
  left_join(target.ball.data.con%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_con=x_l_approx, x_r_target_con=x_r_approx, x_target_con=x_approx))
```

```{r}


gaze_plot_data$condition<-relevel(as.factor(gaze_plot_data$condition), "hab", "exp", "con")

con.labs <- c("Familiarisation", "Contact", "No contact")
names(con.labs) <- c(levels(as.factor(gaze_plot_data$condition)))

gaze_contact_plot<-ggplot(data = gaze_plot_data, aes(x = time.frame, y = mean.x)) +
  geom_vline(data = gaze_plot_data %>% filter(condition != "hab"),aes(xintercept=baseline.end), lty=2, alpha=0.6)+
  #target ball
  geom_ribbon(data = gaze_plot_data %>% filter(condition == "con"), aes(x = time.frame, ymin = x_l_target_con, ymax = x_r_target_con), fill = "#14169D", alpha = 0.8) +
  geom_line(data = gaze_plot_data %>% filter(condition == "con"), aes(x = time.frame, y = x_target_con), color = "#14169D") +
  geom_ribbon(data = gaze_plot_data %>% filter(condition == "exp"), aes(x = time.frame, ymin = x_l_target_exp, ymax = x_r_target_exp), fill = "#14169D", alpha = 0.8) +
  geom_line(data = gaze_plot_data %>% filter(condition == "exp"), aes(x = time.frame, y = x_target_exp), color = "#14169D") +
  #launch ball
   geom_ribbon(data = gaze_plot_data %>% filter(condition != "hab"), aes(x = time.frame, ymin = x_l_launch, ymax = x_r_launch), fill = "#d1bd19", alpha = 0.8) +
  geom_line(data = gaze_plot_data %>% filter(condition != "hab"), aes(x = time.frame, y = x_launch), color = "#d1bd19") + 
  geom_ribbon(data = gaze_plot_data %>% filter(condition == "hab"), aes(x = time.frame, ymin = x_l_launch_hab, ymax = x_r_launch_hab), fill = "#d1bd19", alpha = 0.8) +
  geom_line(data = gaze_plot_data %>% filter(condition == "hab"), aes(x = time.frame, y = x_launch_hab), color = "#d1bd19") +
  #gaze
  geom_path(data = gaze_plot_data %>% filter(condition == "hab", time.frame<4500), aes(y = median.x), size = 1.2, alpha = 0.8) +
  geom_ribbon(data = gaze_plot_data %>% filter(condition == "hab", time.frame<4500), aes(ymin = mean.x - se.x, ymax = mean.x + se.x), alpha = 0.3)+
 #   geom_point(data = gaze_plot_data %>% filter(condition != "hab"), alpha = 0.4,  size=0.5) +
  geom_point(alpha = 0.1, size=0.5) +
  geom_path(data = gaze_plot_data %>% filter(condition != "hab"), aes(y = median.x), size = 1.2, alpha = 0.8) +
        geom_ribbon(data = gaze_plot_data %>% filter(condition != "hab"), aes(ymin = mean.x - se.x, ymax = mean.x + se.x), alpha = 0.4)+
     facet_wrap(~condition,labeller=labeller(condition=con.labs)) +
   ylab("Horizontal coordinates (in px)") +
  xlab("Time (in ms)") +
  xlim(0, 13517)+
  ylim(0, 1024)+
    theme_bw()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 12))


gaze_contact_plot

```



#### Dwell time plot
```{r}
xdata <- read_csv("data/causal_perception_dwell_time_data.csv")
```

* End IP
```{r}
test.IP.end.IA.balls.data<-xdata%>%
  filter(IA_LABEL=="IA_end_launch_ball",  condition!="hab", IP_LABEL=="end_IP")%>%
  mutate(condition.new=fct_recode(as.factor(condition), "No contact"="exp", "Contact"="con"))


test.IP.end.IA.balls.data$condition2 <- jitter(as.numeric(as.factor(test.IP.end.IA.balls.data$condition), amount = .0001))
y_lim_min<-0
y_lim_max<-10000

library(gghalves)


plot_end_balls <- ggplot(data = test.IP.end.IA.balls.data, aes(x = condition.new, y= IA_DWELL_TIME)) +
  #Add geom_() objects
   geom_point(data = test.IP.end.IA.balls.data %>% filter(condition.new =="Contact"), aes(x = condition2), color = 'darkorange', size = 1.5, 
              alpha = .5) +
   geom_point(data = test.IP.end.IA.balls.data %>% filter(condition.new =="No contact"), aes(x = condition2), color = 'dodgerblue', size = 1.5, 
              alpha = .5) +
   geom_line(aes(x = condition2, group = subject), color = 'lightgray', alpha = .5) +
  
   geom_half_boxplot(
     data = test.IP.end.IA.balls.data %>% filter(condition.new=="Contact"), aes(x=condition2, y = IA_DWELL_TIME), position = position_nudge(x = -.4), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .1, 
     fill = 'darkorange', alpha = .5) +
   
   geom_half_boxplot(
     data = test.IP.end.IA.balls.data %>% filter(condition.new=="No contact"), aes(x=condition2, y = IA_DWELL_TIME), position = position_nudge(x = .25), 
     side = "r",outlier.shape = NA, center = TRUE, errorbar.draw = TRUE, width = .1, 
     fill = 'dodgerblue', alpha = .5) +
   #Define additional settings
   scale_x_continuous(breaks=c(1,2), labels=c("Contact", "No contact"), limits=c(0.4, 2.5)) +
   xlab("") + ylab("Dwell time (in ms)") +
  # ggtitle('Cube: end position') +
    theme_bw()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
   coord_cartesian(ylim=c(y_lim_min, y_lim_max))
  
plot_end_balls 
 

```
*Plot grid
```{r}
pg.contact.gaze<-plot_grid(gaze_contact_plot,plot_end_balls , ncol=2,nrow=1, rel_widths = c(3,1.2), labels=c("C", "D"))

pg.contact2<-plot_grid(pg.contact.gaze,pg_contact, ncol=1)
```


#### Adding screenshots

```{r}
library(cowplot)
contact_exp_ini_photo <- "screenshots/contact_exp_ini.jpg"
contact_con_ini_photo <- "screenshots/contact_con_ini.jpg"
contact_exp_mid_photo <- "screenshots/contact_exp_mid.jpg"
contact_exp_fin_photo <- "screenshots/contact_exp_fin.jpg"
contact_con_mid_photo <- "screenshots/contact_con_mid.jpg"
contact_con_fin_photo <- "screenshots/contact_con_fin.jpg"

contact_exp_ini <- ggdraw(theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))) + draw_image(contact_exp_ini_photo)
contact_con_ini <- ggdraw(theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))) + draw_image(contact_con_ini_photo)
contact_exp_mid <- ggdraw(theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))) + draw_image(contact_exp_mid_photo)
contact_exp_fin <- ggdraw(theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))) + draw_image(contact_exp_fin_photo)
contact_con_mid <- ggdraw(theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))) + draw_image(contact_con_mid_photo)
contact_con_fin <- ggdraw(theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))) + draw_image(contact_con_fin_photo)

contact_pics_exp<-plot_grid(contact_exp_ini, contact_exp_mid, contact_exp_fin, ncol=3)
contact_pics_con<-plot_grid(contact_con_ini, contact_con_mid, contact_con_fin, ncol=3)
```
#### Combine plot grid

```{r}
pg.contact3<-plot_grid(contact_pics_con, contact_pics_exp, pg.contact2, ncol=1, rel_heights = c(0.5, 0.5, 1.5), labels = c("A", "B", ""), label_colour = "white")

pg.contact3

ggsave(pg.contact3, filename = "graphics/causal_perception_figure1.jpeg", width = 10.5, height=13, scale=0.75, dpi=600)
ggsave(pg.contact3, filename = "graphics/causal_perception_figure1.pdf", width = 10.5, height=13, scale=0.75)
```

## Dynamic AoI analysis: r-squared

#### target ball
```{r}
data.r2.target <- sample.data %>%
  filter(time.frame > 933 & time.frame < 3482) %>%
  mutate(phase2 = ifelse(session.num == 2 & phase == "hab1", "hab4", ifelse(session.num == 2 & phase == "hab2", "hab5", ifelse(session.num == 2 & phase == "hab3", "hab6", ifelse(phase == "test", condition, phase))))) %>%
  group_by(phase2, condition, time.frame, subject) %>%
  summarise(mean.x = mean(RIGHT_GAZE_X), mean.y = mean(RIGHT_GAZE_Y), mean.pupil = mean(RIGHT_PUPIL_SIZE)) %>%
    left_join(launch.ball.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch=x_l_approx, x_r_launch=x_r_approx, x_launch=x_approx))%>%
  left_join(launch.ball.data.hab%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch_hab=x_l_approx, x_r_launch_hab=x_r_approx, x_launch_hab=x_approx))%>%
  left_join(target.ball.data.exp%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_exp=x_l_approx, x_r_target_exp=x_r_approx, x_target_exp=x_approx))%>%
  left_join(target.ball.data.con%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_con=x_l_approx, x_r_target_con=x_r_approx, x_target_con=x_approx))
```

```{r}
library(broom)
r2.exp <- data.r2.target %>%
  droplevels() %>%
  filter(phase2=="exp")%>%
  nest(-subject, -phase2) %>%
  mutate(
    fit = map(data, ~ lm(mean.x ~ x_target_exp, data = .)),
    results = map(fit, glance)
  ) %>%
  unnest(results) %>%
  select(subject, phase2, r.squared) %>%
  rename(r.sq.exp = r.squared) %>%
  mutate(across(where(is.numeric), round, 3))%>%
  ungroup()%>%
  select(-phase2)


r2.con <- data.r2.target %>%
  filter(phase2=="con")%>%
  droplevels() %>%
  nest(-subject, -phase2) %>%
  mutate(
    fit = map(data, ~ lm(mean.x ~ x_target_con, data = .)),
    results = map(fit, glance)
  ) %>%
  unnest(results) %>%
  select(subject, r.squared) %>%
  rename(r.sq.con = r.squared) %>%
  mutate(across(where(is.numeric), round, 3))%>%
  ungroup()%>%
  select(-phase2)

r2.exp %>%
  summarise(mean = mean(r.sq.exp),median = median(r.sq.exp), min = min(r.sq.exp), max = max(r.sq.exp), sd = sd(r.sq.exp))

r2.con %>%
  summarise(mean = mean(r.sq.con), median = median(r.sq.con), min = min(r.sq.con), max = max(r.sq.con), sd = sd(r.sq.con))

```
Comparing r2 values for target ball across the two condition
```{r}

r2_target<-r2.exp%>%full_join(r2.con )
t.test(r2_target$r.sq.exp, r2_target$r.sq.con, paired=TRUE)

```
Determine r² values for the entire sample:
```{r}
r2.exp.target.group=lmer(mean.x~x_target_exp+(1|subject), data =  data.r2.target%>%filter(phase2=="exp"),REML=F)
summary(r2.exp.target.group)

library(MuMIn)
r.squaredGLMM(object=r2.exp.target.group)


r2.con.target.group=lmer(mean.x~x_target_con+(1|subject), data =  data.r2.target%>%filter(phase2=="con"),REML=F)
summary(r2.con.target.group)

r.squaredGLMM(object=r2.con.target.group)
```


launch ball
```{r}

data.r2.launch <- sample.data %>%
  filter(time.frame < 933 & time.frame > 500) %>%
  mutate(phase2 = ifelse(session.num == 2 & phase == "hab1", "hab4", ifelse(session.num == 2 & phase == "hab2", "hab5", ifelse(session.num == 2 & phase == "hab3", "hab6", ifelse(phase == "test", condition, phase))))) %>%
  group_by(phase2, condition, time.frame, subject) %>%
  summarise(mean.x = mean(RIGHT_GAZE_X), mean.y = mean(RIGHT_GAZE_Y), mean.pupil = mean(RIGHT_PUPIL_SIZE)) %>%
    left_join(launch.ball.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch=x_l_approx, x_r_launch=x_r_approx, x_launch=x_approx))%>%
  left_join(launch.ball.data.hab%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch_hab=x_l_approx, x_r_launch_hab=x_r_approx, x_launch_hab=x_approx))%>%
  left_join(target.ball.data.exp%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_exp=x_l_approx, x_r_target_exp=x_r_approx, x_target_exp=x_approx))%>%
  left_join(target.ball.data.con%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_con=x_l_approx, x_r_target_con=x_r_approx, x_target_con=x_approx))

r2.exp <- data.r2.launch %>%
  droplevels() %>%
  filter(phase2=="exp"|phase2=="con")%>%
  nest(-subject, -phase2) %>%
  mutate(
    fit = map(data, ~ lm(mean.x ~ x_launch, data = .)),
    results = map(fit, glance)
  ) %>%
  unnest(results) %>%
  select(subject, phase2, r.squared) %>%
  rename(r.sq.exp = r.squared) %>%
  mutate(across(where(is.numeric), round, 3))

r2.exp %>%
  group_by(phase2) %>%
  summarise(mean = mean(r.sq.exp), median = median(r.sq.exp),min = min(r.sq.exp), max = max(r.sq.exp), sd = sd(r.sq.exp))

```
Comparing r2 values for target ball across the two condition
```{r}
r2.launch<-r2.exp%>%
  pivot_wider(names_from = phase2, values_from=r.sq.exp)

t.test(r2.launch$exp, r2.launch$con, paired=TRUE)

```
Determine r² values for the entire sample:
```{r}
r2.exp.launch.group=lmer(mean.x~x_launch+(1|subject), data =  data.r2.launch%>%filter(phase2=="exp"),REML=F)
summary(r2.exp.launch.group)

library(MuMIn)
r.squaredGLMM(object=r2.exp.launch.group)


r2.con.launch.group=lmer(mean.x~x_launch+(1|subject), data =  data.r2.launch%>%filter(phase2=="con"),REML=F)
summary(r2.con.launch.group)

r.squaredGLMM(object=r2.con.launch.group)
```

launch ball: familiarisation
```{r}

data.ind.hab <- sample.data %>%
  filter(time.frame < 3486 & time.frame > 500) %>%
  mutate(phase2 = ifelse(session.num == 2 & phase == "hab1", "hab4", ifelse(session.num == 2 & phase == "hab2", "hab5", ifelse(session.num == 2 & phase == "hab3", "hab6", ifelse(phase == "test", condition, phase))))) %>%
  group_by(phase2, condition, time.frame, subject) %>%
  summarise(mean.x = mean(RIGHT_GAZE_X), mean.y = mean(RIGHT_GAZE_Y), mean.pupil = mean(RIGHT_PUPIL_SIZE)) %>%
    left_join(launch.ball.data%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch=x_l_approx, x_r_launch=x_r_approx, x_launch=x_approx))%>%
  left_join(launch.ball.data.hab%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_launch_hab=x_l_approx, x_r_launch_hab=x_r_approx, x_launch_hab=x_approx))%>%
  left_join(target.ball.data.exp%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_exp=x_l_approx, x_r_target_exp=x_r_approx, x_target_exp=x_approx))%>%
  left_join(target.ball.data.con%>%select(time.frame, x_l_approx, x_r_approx, x_approx)%>%rename(x_l_target_con=x_l_approx, x_r_target_con=x_r_approx, x_target_con=x_approx))

r2.hab <- data.ind.hab %>%
  droplevels() %>%
  filter(condition=="hab")%>%
  nest(-subject, -condition) %>%
  mutate(
    fit = map(data, ~ lm(mean.x ~ x_launch_hab, data = .)),
    results = map(fit, glance)
  ) %>%
  unnest(results) %>%
  select(subject, condition, r.squared) %>%
  rename(r.sq.hab = r.squared) %>%
  mutate(across(where(is.numeric), round, 3))

r2.hab %>%
  group_by(condition) %>%
  summarise(mean = mean(r.sq.hab), median = median(r.sq.hab),min = min(r.sq.hab), max = max(r.sq.hab), sd = sd(r.sq.hab))

```

Determine r² values for the entire sample:
```{r}
r2.hab.group=lmer(mean.x~x_launch_hab+(phase2|subject), data =  data.ind.hab%>%filter(condition=="hab"),REML=F)
summary(r2.hab.group)

library(MuMIn)
r.squaredGLMM(object=r2.hab.group)
```
### LMM
* read data 
```{r}
exp.data.pupil.lmer <- read_csv("data/causal_perception_pupil_size_aggregated_data.csv")
```

```{r}
exp.data.pupil.lmer$z.dev<-scale(exp.data.pupil.lmer$mean.deviation)#mean deviation from center
exp.data.pupil.lmer$z.age<-scale(exp.data.pupil.lmer$age)
hist(exp.data.pupil.lmer$pupil.size.corrected)

```


```{r}
mm1.pupil<-lmer(pupil.size.corrected~condition+z.age+z.dev+Order_condition+ (1+z.dev||subject), REML=F, data=exp.data.pupil.lmer)

summary(mm1.pupil)

```

* Assumptions
```{r}
diagnostics.plot(mm1.pupil)

ranef.diagn.plot(mm1.pupil)

library(car)

xx=lm(pupil.size.corrected~condition+z.age+z.dev+Order_condition, data=exp.data.pupil.lmer)
vif(xx)
```

Model stability 
```{r}

full.stab=glmm.model.stab(model.res=mm1.pupil, contr=NULL, para=F,
data=NULL)

table(full.stab$detailed$warnings)

round(full.stab$summary[, -1], 3)

m.stab.plot(full.stab$summary [, -1])
```
*Likelihood ratio tests
```{r}
tests=as.data.frame(drop1(mm1.pupil, test="Chisq"))
round(tests, 3)
```
* CI
```{r}

boot.full=boot.glmm.pred(model.res=mm1.pupil, excl.warnings=F,
nboots=1000, para=T, n.cores=3, resol=1000, level=0.95)

round(boot.full$ci.estimates, 2)
m.stab.plot(boot.full$ci.estimates)
```




```{r}
save.image(file="AP_ball_pupil_size_workspace.RData")
```




